% -*- coding: utf-8 -*-

\part{Specifications Database}

\chapter{Overview}

\paragraph{%
In knowing how to maintain any system, it is critical to know what the expected %
behaviour of that system is. Hence, this section of the book contains data on the %
stock configuration of all Old World Macintosh models (Performa-branded %
Macintoshes are not covered due to their being variations on a base model, %
a full listing will be present.) % 
}

\paragraph{%
This database is chiefly divided into two segments, for ease of navigation. The %
first, ``68k Macintoshes'', covers Macintoshes making use of the Motorola 68000 %
series microprocessors. These are identified by a lack of \textsl{\textbf{\textrm{PowerPC}}} %
branding on the case of the machine. The second segment, ``PowerPC Macintoshes'', %
covers Power Macintoshes and PowerBooks bearing the \textsl{\textbf{\textrm{PowerPC}}} logo; % 
these machines make use of a high-performance RISC CPU series principally designed by IBM. %
}

\paragraph{%
The data in the following pages is definitive, verified against multiple sources, including %
(where possible) the author's own collection. For machines not in the author's collection, %
data is provided based on at least two sources, three if possible, in order to minimise the %
risk of false information. The only disputable data is what constitutes the ``Optimal'' %
System Software version for a given Macintosh; this is based on the author's own %
experience and is entirely arbitrary. Caveat lector, your mileage may vary. %
}

\cleardoublepage
\input{01b_meta68k.tex}

\cleardoublepage
\input{01c_metappc.tex}